---
title: "Data 607 Assignment 3"
author: "Jayden Jiang"
date: "2025-02-20"
output: html_document
---

```{r}
library(dplyr)
library(stringr)
library(readr)
```

### Normalization
```{r}
# Create dataframe
car_sales <- data.frame(
  customer_name = c("John", "Sharon", "Shirley", "Daniel", "Jay"),
  customer_phone = c("111-2222", "111-3333", "111-4444", "111-5555", "111-6666"),
  car_vin = c("VIN001", "VIN002", "VIN003", "VIN004", "VIN005"),
  car_make = c("Mazeda", "Honda", "Lexus", "Tesla", "Benz"),
  car_model = c("CX-5", "CRV", "RX-350", "Model-Y", "GLE"),
  car_year = c("2020", "2019", "2024", "2023", "2023"),
  salesperson_name = c("Evan T.", "Fiona W.", "George K.", "Jessica W.", "Paige E."),
  sale_date = as.Date(c("2025-01-28", "2025-01-28", "2025-01-28", "2025-01-28", "2025-01-28")),
  sale_price = c(20000, 18000, 50000, 35000, 56000)
)
print(car_sales)
```

```{r}
# Customer Table
customers <- car_sales %>%
  select(customer_name, customer_phone) %>%
  distinct()

print(customers)
```
```{r}
# Cars Table
cars <- car_sales %>%
  select(car_vin, car_make, car_model, car_year) %>%
  distinct()

print(cars)
```
```{r}
# Sales Table
sales <- car_sales %>%
  select(customer_name, customer_phone, car_vin, salesperson_name, sale_date, sale_price)

print(sales)
```
### Character Manipulation
```{r}
majors_data <- read.csv("https://raw.githubusercontent.com/JaydeeJan/Data-607-Assignment-3/refs/heads/main/majors-list.csv")

data_stats_majors <- majors_data %>%
  filter(str_detect(Major, regex("DATA|STATISTICS", ignore_case = TRUE)))

print(data_stats_majors)
```

### Describe, in words, what these expressions will match:

### (.)\1\1

#### 1. (.) - will match any single character in first group

#### 2. \1 - refers to the match contained in the first parenthesis

#### 3. \1\1 - character repeated two or more times. 


### "(.)(.)\\2\\1"

#### 1. (.)(.) - will match any single character in first group and second group

#### 2. \\2 refers to the match contained in the second parenthesis

#### 3. \\1 refers to the match contained in the first parenthesis


### (..)\1

#### 1. (..) - match with two characters

#### 2. \1 - refers to the match contained in the first parenthesis


### "(.).\\1.\\1"

#### 1. (.) -  will match any single character in first group

#### 2. . - match any character

#### 3. \\1 - refers to the match contained in the first parenthesis

#### 4. . - match any character

#### 5. \\1 - refers to the match contained in the first parenthesis


### "(.)(.)(.).*\\3\\2\\1"

#### 1. (.) - will match any single character in first group

#### 2. (.) - will match any single character in second group

#### 3. (.) - will match any single character in third group

#### 4. .* - will match any sequence of characters

#### 5. \\3 - refers to the match contained in the third parenthesis

#### 6. \\2 - refers to the match contained in the second parenthesis

#### 7. \\1 - refers to the match contained in the first parenthesis



### Construct regular expressions to match words that:

#### Start and end with the same character.

#### (.)\1

#### Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

#### "(..).*\\1"

#### Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

#### "(.)\\1.*\\1"



